Differential invariant signatures for planar Lie group transformations of images

### 2019-09-05 paper/newpaper.tex
Minor improvements...

Is this helpful? 
\todo[inline]{Yes, this is helpful but not quite correct yet - $SE(2)$ is missing, and we need edges from $\text{Diff}_{\text{vol}}$ to the special affine and Euclidean groups}
\todo[inline]{Other notes: should our projective group be $PGL(3, \mathbb{R})$ rather than $PSL(3, \mathbb{R})$? or am I confused?}
\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]
\node(C1) [] {Diff};
\node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
\node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
\node(A1) [below right of=C3]                          {$PSL(2,\mathbb{C})$};
\node(B1)    [below of=C2]    {$PSL(3,\mathbb{R})$};
\node(B2)   [below of=B1]              {$A(2)$};
\node(A2)       [below left of=A1]          {Sim$(2)$};
\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
\node(B3)   [below of=B2]            {$SA(2)$};
\node(A4)      [below of=A2]            {$E(2)$};
\node(A5) [below right of=A4]{Translation};

\draw[thick,->] (C1) to  (C2);
\draw[thick,->] (C1) to  (C3);
%\draw[thick,->] (C1) to  (A2);
\draw[thick,->] (C3) to  (A1);
\draw[thick,->] (A1)   to (A2);
\draw[thick,->] (A1)    to (A3);
\draw[thick,->] (B1) to  (B2);
\draw[thick,->] (B2) to  (B3);
\draw[thick,->] (A2) to  (A4);
\draw[thick,->] (B3) to  (A4);
\draw[thick,->] (A3) to  (A5);
\draw[thick,->] (A4) to  (A5);
\end{tikzpicture}
\end{center}
\caption{The lattice of groups considered in this paper. The edges identify subgroups.}
\end{figure}

@@

E2:
{\bf Aside 3. Role of the invariants} 
All of the 2nd order differential invariants play known roles in geometric analysis:
\begin{enumerate}
\item $f_if_i=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
\item $f_{ii}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
\item $f_{ij}f_i f_j$ is the `infinity-Laplacian'; critical points of $\|\nabla f\|_{L^\infty}$ obey the PDE $f_{ij}f_i f_j=0$;
\item
$f_{ij}f_i f_j$ is also a Lagrangian density for $-2\det f_{ij}$, which arises in Monge--Amp\`ere equations and
which can be written in terms of the final 2nd order invariant as $-2 \det f_{ij} = f_{ij}f_{ij}-f_{ii}^2$.
\end{enumerate}
In addition, we shall see in later sections that functions of these invariants are invariants or
relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.

@@

Olver uses the group $SE(2)$ as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant. We demonstrate the method with two groups: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).

@@

The 0th order moving frame translates $z$ to $\beta$. We can therefore take $\beta=0$; we are also free to take $\delta=1$. This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.

@@

The moving frame calculation now proceeds as follows.
\begin{enumerate}
\item The frame $\bar f_x=1$, $\bar f_y=0$ determines the group parameters
$$ a = f_x/(f_i f_i),\quad b = f_y/(f_i f_i).$$

\item The frame $\bar f_{xyy}=\bar f_{yy}=0$ determines the group parameters
$$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_i f_i)^2$$
$$ d = (f_{xyy}f_x^2 - f_x f_y f_{xx} - f_{xyy}f_y^2 - f_{yy} f_x f_y)/(2 f_i f_i)^2.$$

\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is 
$$\bar f_{xx} = \frac{f_{ii}}{f_i f_i}.$$

\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \bar f_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
\end{enumerate}

>>>>

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=2cm]
\node(C1) [] {Diff};
\node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
\node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
\node(B1)    [below of=C1]    {$PSL(3,\mathbb{R})$};
\node(A1) [below of=C3]                          {$PSL(2,\mathbb{C})$};
\node(B2)   [below of=B1]              {$A(2)$};
\node(A2)       [below right of=B2]          {Sim$(2)$};
%\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
\node(B3)   [below left of=B2]            {$SA(2)$};
\node(A4)      [below of=A2]            {$E(2)$};
\node(A6)      [below left of=A4]            {$SE(2)$};
\node(A5) [below of=A6]{$T(2)$};

\draw[thick,->] (C1) to  (C2);
\draw[thick,->] (C1) to  (C3);
\draw[thick,->] (C1) to  (B1);
\draw[thick,->] (C2) to  (B3);
%\draw[thick,->] (C1) to  (A2);
\draw[thick,->] (C3) to  (A1);
\draw[thick,->] (A1)   to (A2);
\draw[thick,->] (B1) to  (B2);
\draw[thick,->] (B2) to  (B3);
\draw[thick,->] (B2) to  (A2);
\draw[thick,->] (A2) to  (A4);
\draw[thick,->] (B3) to  (A6);
\draw[thick,->] (A4) to  (A6);
\draw[thick,->] (A6) to  (A5);
\end{tikzpicture}
\end{center}
\caption{The lattice of groups considered in this paper. The edges identify subgroups.}
\end{figure}

@@

E2:
{\bf Aside 3. Role of the invariants} 
All of the 2nd order differential invariants play known roles in geometric analysis:
\begin{enumerate}
\item $f_x^2 + f_y^2=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
\item $f_{xx} + f_{yy}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is the `infinity-Laplacian'; 
\item $f_{xx}f_x^2 + 2 f_{xy} f_x f_y + f_{yy} f_y^2 $ is also a Lagrangian density for $-2(f_{xx} f_{yy} - f_{xy}^2)$, which arises in the Monge--Amp\`ere equations and
can be written in terms of the final 2nd order invariant as $-2 (f_{xx} f_{yy} - f_{xy}^2) = 2 f_{xy}^2 - f_{xx}^2 - f_{yy}^2$
\end{enumerate}
In addition, we shall see in later sections that functions of these invariants are invariants or
relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.

@@

Olver uses the group $SE(2)$ on curves as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant. We demonstrate the method with two groups: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).

@@

The 0th order moving frame translates $z$ to $\beta$. We can therefore take $\beta=0$; we are also free to take $\delta=1$. This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
\todo[inline]{General thm for this earlier...}

@@

The moving frame calculation now proceeds as follows.
\begin{enumerate}
\item The frame $\bar f_x=1$, $\bar f_y=0$ determines the group parameters
$$ a = f_x/(f_x^2 + f_y^2),\quad b = f_y/(f_x^2 f_y^2).$$

\item The frame $\bar f_{xy}=\bar f_{yy}=0$ determines the group parameters
$$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_x^2 + f_y^2)^2$$
$$ d = (f_{xy}f_x^2 - f_x f_y f_{xx} - f_{xy}f_y^2 - f_{yy} f_x f_y)/(2 f_x^2 + f_y^2)^2.$$

\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is 
$$\bar f_{xx} = \frac{f_{xx}+f_{yy}}{f_x^2 + f_y^2}.$$

\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \bar f_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
rational functions with numerators of degree 6 and denominators $(f_x^2 + f_y^2)^4$, and are relative invariants of weight 8.
\end{enumerate}
